---
title       : Process Analysis
subtitle    : Shiny App at Work
author      : Mariusz Musiał
job         : 
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
revealjs    :
    theme   : Solarized
    transition : convex
---
```{r echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(dplyr)

load("../procdata.RData") # load the dataframe

procdata <- procdata %>% filter(Process %in% c("A", "B", "C", "D"))
procdata2 <- procdata[sample(nrow(procdata), size = 20, replace = F),]
```


```{r cache=F,echo=F}
# https://gist.github.com/srvanderplas/68d73ee4c6fdead4ed32
# 
c0 <- knitr::knit_hooks$get('chunk')

knitr::knit_hooks$set(
  list(
    chunk=function(x,options){
      if(is.null(options$class) & is.null(options$fragIndex)){
        c0(x, options)
      } else if(is.null(options$fragIndex)) {
        classidx <- which(names(options)=="class")
        paste0(
          paste0("<span class='", options$class, "'>"),
          c0(x, options[-classidx]),
          '</span>\n'
        )
      }
      else if(length(options$fragIndex)==1) {
        classidx <- which(names(options)%in%c("class", "fragIndex"))
        str_replace(
          paste0(
            paste0("<span class='", options$class, "' data-fragment-index=", options$fragIndex,">"),
            c0(x, options[-classidx]),
            '</span>\n'
          ),
          "<div class=\"chunk\" id=\"(.*?)\">\\s*<div class=\"rimage default\">(.*)</div>\\s*</div>",
          "\\2"
        )
      } else {
        classidx <- which(names(options)%in%c("class", "fragIndex"))
        str_replace(
          paste0(
            paste0("<span class='", options$class, " fade-in' data-fragment-index=", options$fragIndex[1],">"),
            paste0(
              paste0("<span class='", options$class, " fade-out' data-fragment-index=", options$fragIndex[2],">"),
              c0(x, options[-classidx]),
              '</span>\n'
              ),
            '</span>\n'
            ),
          "<div class=\"chunk\" id=\"(.*?)\">\\s*<div class=\"rimage default\">(.*)</div>\\s*</div>",
          "\\2"
        )
        
      }
        
    }
  )
)
```

## Process Analysis

<span style="color:green">
*A Developing Data Products Assignment Project*
</span>

--- .class #id

## Process Analysis App

### It will help you:

<ul style="list-style-type:circle">
    <div class="fragment">
        <li>to get the overview of statistical parameters</li>
    </div>
    <div class="fragment">
        <li>to transform the data</li>
    </div>
        <div class="fragment">
        <li>to select time range</li>
    </div>
    <div class="fragment">
        <li>to view the distribution and scatterplots</li>
    </div>
    <div class="fragment">
        <li>to test for means equality</li>
    </div>
    <div class="fragment">
        <li>to test for trend change over time</li>
    </div>
</ul>
<br>
<div class="fragment">
    <span style="color:green">
        <small><q>Process Analysis App just does this. It helps to analyze and compaer functionally equivalent processes.
        </q></small>
    </span>
</div>

---

## Analyze data in two domains

*** {name: left}
Poulation

```{r, echo=FALSE, class="fragment"}
        ga <- ggplot(procdata, aes(x = Process, y = Performance, fill = Process))
        ga <- ga + geom_violin()
        ga <- ga + geom_boxplot(fill = "grey", color = "red", outlier.colour = "red",
                                outlier.size = 3, width = .2)
        ga <- ga + stat_summary(color = "black", fun.y=mean, geom="point", shape=21, size=4)
        ga <- ga + ggtitle("Process Performance")
        ga <- ga + xlab("Process type")
            ga <- ga + ylab("Performance metric")
        ga <- ga + theme(plot.title = element_text(size = rel(2), 
                                                   colour = "darkblue", face = "bold"))
        ga <- ga + theme(axis.title.y = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.title.x = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.text.x = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.text.y = element_text(size = rel(1.5)))
        ga
```

*** {name: right}
Time

```{r, echo=FALSE, class="fragment"}
    g8 <- ggplot(procdata, aes(x = Date, y = Performance, color = Process))
    g8 <- g8 + geom_point(size = 3, alpha = .6)
    g8 <- g8 + geom_smooth(method = "lm", color = "black")
    g8 <- g8 + facet_wrap(~Process)
    g8 <- g8 + ggtitle("Performance trends per Process Type")
    g8 <- g8 + xlab("Process run date")
    g8 <- g8 + ylab("Performance metric")
    g8 <- g8 + theme(legend.position="none")
    g8 <- g8 + theme(axis.text.x = element_text(angle = 90))
    g8 <- g8 + theme(plot.title = element_text(size = rel(2), 
                                               colour = "darkblue", face = "bold"))
    g8 <- g8 + theme(axis.title.y = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.title.x = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.text.x = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.text.y = element_text(size = rel(1.5)))

    g8
```


--- .class #id 

## Review some selected statistics in a tabular form

```{r, echo=FALSE, results='asis'}
# Hint from https://github.com/ramnathv/slidify/issues/414
# 
dynamic_table <- DT::datatable(procdata2[,1:4],
                               options = list(autoWidth = FALSE,
                                              searching = TRUE,
                                              paging = TRUE,
                                              info = FALSE,
                                              pageLength = 5,
                                              ordering = TRUE)
                               )
DT::saveWidget(dynamic_table, 'example.html')
cat('<iframe src="example.html" STYLE="width:100%" height="420"> </iframe>')
```

<small>The table is live, check it out!</small>

--- .class #id 

## Where to find the stuff?

<ul style="list-style-type:circle">
    <li><a href="https://marioem.shinyapps.io/ProcessAnalysis/">Process Analysis App</a></li>
    <li><a href="https://github.com/marioem/DevelopingDataProducts/tree/master">App code on GitHub</a></li>
    <li><a href="">Presentation code on GitHub</a></li>
</ul>
<br>
<span style="color:green">
*A simple documentation about the app is embedded in the app itself*
</span>

